Truth space method for caching database queries

### 2015-03-01 english_version/MAIS/paper_main.tex
MAIS version modified

%%
\date{April 15, }\ydate{2013}
\firstpage{175}

@@

\UDC{519.987} \shorttitle{Truth space method for caching database queries}
\affiliation{\small Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences, \\Pevtsova str., 13, Omsk, 644043, Russia}
\ruaffiliation{\small Омский филиал Федерального государственного бюджетного учреждения науки Института математики им. С.Л.~Соболева Сибирского отделения Российской академии наук \\644043, Россия, г. Омск,
ул. Певцова, 13,}
%%%%
\email{svmosin@gmail.com, szykin@mail.ru}
\authorinform{
\textbf{Мосин Сергей Владимирович},\\Омский филиал Федерального государственного бюджетного учреждения науки Института математики им. С.Л.~Соболева Сибирского отделения Российской академии наук, аспирант\\
\textbf{Зыкин Сергей Владимирович},\\Омский филиал Федерального государственного бюджетного учреждения науки Института математики им. С.Л.~Соболева Сибирского отделения Российской академии наук, д-р техн. наук, профессор
}

@@

\renewcommand{\refname}{References}
\bibliography{references}

>>>>

%%
\date{March 1, }\ydate{2015}
%\firstpage{175}

@@

\UDC{519.987} \shorttitle{Truth space method for caching database queries}
\affiliation{\small Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences, \\Pevtsova str., 13, Omsk, 644043, Russia}
\ruaffiliation{\small Омский филиал Федерального государственного бюджетного учреждения науки Института математики им. С.Л.~Соболева Сибирского отделения Российской академии наук \\644043, Россия, г. Омск,
ул. Певцова, 13,}
%%%%
\email{svmosin@gmail.com, szykin@mail.ru}
\authorinform{
\textbf{Мосин Сергей Владимирович},\\Федеральное государственне бюджетное учреждение науки Институт математики им. С.Л.~Соболева Сибирского отделения Российской академии наук (Омский филиал), аспирант\\
\textbf{Зыкин Сергей Владимирович},\\Федеральное государственне бюджетное учреждение науки Институт математики им. С.Л.~Соболева Сибирского отделения Российской академии наук (Омский филиал), д-р техн. наук, профессор
}

@@

\renewcommand{\refname}{References}
\begin{thebibliography}{1}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{zyk_pol}
S.~Zykin, A.~Poluyanov, Multidimensional data building using intermediate
  representations., Administration problems~(5) (2013) 54--59.

\bibitem{chang}
C.-S. Park, M.-H. Kim, Y.-J. Lee, Usability-based caching of query results in
  olap systems., Journal of Systems and Software 68~(2) (2003) 103--119.

\bibitem{baralis}
E.~Baralis, S.~Paraboschi, E.~Teniente,
  \href{http://dl.acm.org/citation.cfm?id=645923.671019}{Materialized views
  selection in a multidimensional database}, in: Proceedings of the 23rd
  International Conference on Very Large Data Bases, VLDB '97, Morgan Kaufmann
  Publishers Inc., San Francisco, CA, USA, 1997, pp. 156--165.
\newline\urlprefix\url{http://dl.acm.org/citation.cfm?id=645923.671019}

\bibitem{kalnis}
P.~Kalnis, D.~Papadias, Proxy-server architectures for olap., in: S.~Mehrotra,
  T.~K. Sellis (Eds.), SIGMOD Conference, ACM, 2001, pp. 367--378.

\bibitem{Afrati06}
F.~N. Afrati, C.~Li, P.~Mitra, Rewriting queries using views in the presence of
  arithmetic comparisons., Theor. Comput. Sci. 368~(1-2) (2006) 88--123.

\bibitem{Keller96}
A.~M. Keller, J.~Basu, A predicate-based caching scheme for client-server
  database architectures, VLDB J. 5~(1) (1996) 35--47.

\bibitem{shim}
J.~Shim, P.~Scheuermann, R.~Vingralek, Dynamic caching of query results for
  decision support systems., in: SSDBM, 1999, pp. 254--263.

\end{thebibliography}
